\section{Sprint 1: First iteration}
In this section, we will present and discuss the development that took place in the first iteration of our project. This includes a relevant presentation of the Scrum methodology as we have applied it in the sprint. We will mostly present artifacts created that are relevant to the inception and elaboration phases of the unified process.
\subsection{Scrum}
Scrum is an iterative framework designed to manage software development projects \cite{scrumguide} \\
The methods originally intends to include a team of up to eight persons, along with a Scrum Master and a Product Owner. However, as we were only five persons we had no choice but to appoint these roles to team members. Moreover, we decided that we wanted a more democratic approach to the features that we included in our project; this implied that the responsibility of creating product backlog items were spread out on the whole group instead of relying solely on the Product Owner \cite[p.~12]{scrumguide}.
\subsubsection{Initial Scrum}
Before initializing our first sprint, we decided to conduct two sprint planning meetings in somewhat extended versions. Since this were our first project in which we’ve used Scrum, we decided that we would ignore the time bounds that are specified in the Scrum guide \cite[p.~9]{scrumguide}. This allowed us to discuss and familiarize ourselves with the Scrum concepts.\\
The initial meetings were divided into several parts: First, we agreed on using the Scrumwise \cite{scrumwise} tool for organizing our Scrum activities. Then, we all democratically built the product backlog. \\
An important part of the formation of our team before the first sprint were also doing a formal written definition of done. This includes defining a strategy for testing, coding, documentation and acceptance from the rest of the team. The definition of done can be viewed in [section whatever: definition of done]\\
Lastly, we had to agree on the number and length of the sprints we were going to do. This also meant creating an overall timeline of the sprints, which can be viewed in APPENDIX A.1[sprinttimeline.jpeg]  These initial exercises allowed us to conduct the two, more formally defined meetings of sprint planning: part one of two, respectively. \\
A partial view of the product backlog can be found in APPENDIX A.2 [backlog1.jpeg]\\
\subsubsection{Sprint planning $|$ \& $\|$}
After our initial Scrum agreements, we conducted planning meeting part one for the next sprint. This involved several noteworthy items:
\begin{itemize}
\item Creating a capacity plan to get an overview of our initial work capacity [Appendix A.3: Capacity Plan.jpeg]
\item Estimating difficulty and priority of the items on the Product Backlog
\item And elaborating on the meanings of the different backlog items to each other (as part of not having a single product owner).
\end{itemize}
Then moving on to the second part of the meeting, where the team were:
\begin{itemize}
\item committing to highest prioritized tasks and estimating their time to complete
\item distributing the work so the workload was fair on each individual
\item initialize the sprint in the Scrumwise tool and review the burndown chart generated
\end{itemize}
An overview of the first Sprint Backlog is available in [Appendix A.4: Sprint backlog].\\
It is worth nothing that even though we decided on all having influence on the product backlog, the management of the backlog were deferred to one person, the “Product Owner”.\\
\subsubsection{More Scrum}
Our Scrum workflow also covers doing following exercises:\\
\begin{itemize}
\item Doing Daily Scrum meetings, updating burndown charts and reviewing our task boards
\item Updating our product backlog during the sprint so tasks are ready for next sprint
\item Doing the Scrum retrospective and review
\end{itemize}
However, we’ve chosen to defer the description and discussion of these exercises to later sprints where we think they’re more relevant.

\input{texts/Sprint1/InitialSoftwareAnalysis.tex}
\input{texts/Sprint1/InitialDesignArchitecture.tex}
\input{texts/Sprint1/DatabaseDesign.tex}

\newpage