\subsection{Software Architecture}
In this section, we will mainly document our 4+1 artifacts.
\subsubsection{Class Diagrams}
Our product consists of multiple modules (or projects), which each has a large number of classes. Our class diagrams can be seen in the Appendix. There is a class diagram per module.
[Appendix, Illustrations, Class Diagrams, page \pageref{classdiagrams}]
\subsubsection{Sequence Diagrams}
\subsubsection{Package Diagram}
\input{texts/Sprint1/DatabaseDesign.tex}
\subsubsection{Architectural Views}
We have selected the architectural views we find relevant in our project and we’ll briefly define them here before going into detail in separate sections:
\begin{itemize}
\item Logical View: This view summarizes our package architecture as well a brief description of some major components. In this section, we’ll include a UML package diagram and a discussion of the Model-View-Controller pattern.
\item Process View: This view explains the processes and threads
\item Data View: This view explains our persistent data model. We’ll review how we map objects to our relational database and commonly used queries in the database. In this section, we’ll include a UP Data Model and an UML activity diagram(swimlane diagram) that shows our data flow.
\item Deployment View: This view briefly models our physical deployment of the programs. We’ll show network interaction between our components as well as the physical components that we’ll use at the demo presentation. This view will include a deployment diagram.
\item Use Case View: :Maybe we’ll write something here later: Summary of the most significant use-cases and their non-functional requirements. Interaction diagrams can be used and described (System Sequence Diagram)
\end{itemize}
\subsection{Software Architecture Document(SAD)}
\subsubsection{Introduction : Architectural Representation}
This Software Architecture Document(SAD) is meant to be a thorough introduction to the architectural decisions made while designing and implementing the Slice of Pie project @ ITU Fall 2012.\\
One should be familiar with the major decisions regarding the overall structure after reading this document. Please note that for time bounded reasons, this document only contain the parts of a full SAD that are relevant to our project. 